Coherent optical association of a single molecule

### 2020-11-03 paper.tex
Update on Overleaf.

with the other combinations,
and thus requiring an intensity stability of 5\% instead of 0.3\%.
% Thus, instead of a required intensity stability of $0.3 \% $ for the 4422 or 3311 combination, the 3322 combination only requires the intensity to be stabilized to $ 5\% $.

@@

\textcolor{blue}{(clean up the paragraph some more).} %(We might want to mention that those ratios are for 80 kHz spherical trap if we want to give more details about the coupled channel calculation anywhere...)

>>>>

with the other combinations, and thus relaxing the intensity stability requirement to the few percent level. % Thus, instead of a required intensity stability of $0.3 \% $ for the 4422 or 3311 combination, the 3322 combination only requires the intensity to be stabilized to $ 5\% $.

@@

% \textcolor{blue}{(clean up the paragraph some more).} %(We might want to mention that those ratios are for 80 kHz spherical trap if we want to give more details about the coupled channel calculation anywhere...)
